Intrusion Detection with Genetic Algorithms and Fuzzy Logic

### 2013-10-12 paper.tex
Added more to the results section.

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%\terms{Delphi theory}

@@

@@

\subsection{Experimental Design and Results}
The experiments that the authors of~\cite{6496342, 6559603} performed used a total of 16,000 records of normal activity and 10,500 records of attack activity. Of the attack activity, 4,000 of them were denial of service attacks and 6,500 were probe attacks.

@@

>>>>

% A category with the (minimum) three required fields
\category{}{Security and Privacy}{Intrusion Detection Systems}

\terms{}

@@

\mycomment{Explain the 8 features}

@@

\subsection{Experimental Design and Results}
\subsubsection{Experiments using Only RLD09}
The experiments that the authors of~\cite{6496342, 6559603} performed used a total of 16,000 records of normal activity and 10,500 records of attack activity. Of the attack activity, 4,000 of them were denial of service attacks and 6,500 were probe attacks.

@@

In the second experiment, seven tests were run. For each test case there were 13 attack types plus normal activity that were in the training data set. Three attack types were used for the unknown testing data set. For example, the first test case used the training data set that does not have Advance Port Scan, Ack Scan, and Xmas Tree, (which are all probe attacks). These three attacks were then used for the testing data set. Table~\ref{tab:fuzGenExp2} shows some of the results from the fuzzy genetic algorithm and a decision tree algorithm. The fuzzy genetic algorithm has an accuracy of at least 95\% in identifying unknown attacks. When compared with the decision tree algorithm, the fuzzy genetic algorithm has a higher detection rate in all cases except 3 and 5. It can be seen that in cases 2 and 4 the decision tree has low detection rates, while the fuzzy genetic algorithm has much higher detection rates.

\begin{table}
\caption{Unknown Attack Experiment}
\begin{tabular}{|lllcrl|} \hline
Test & Unknown & Decision & & Fuzzy & \\
Case & Attacks & Tree DR & & Genetic DR & \\ \hline

1 & Advance Port Scan & 99.7 & Avg = & 100 & Avg =\\
  & Ack Scan          & 100  & 98.33 & 100 & 100\\
  & Xmas Tree         & 95.3 &       & 100 &\\ \hline

2 & UDP Flood & \textbf{26.7} & Avg = & \textbf{100} & Avg =\\
  & Host Scan & 98.15         & 46.65 & 99.20        & 99.80\\
  & UDP Scan  & \textbf{17.6} &       & \textbf{100} &\\ \hline

3 & Jping    & 100 & Avg =          & 99.20 & Avg =\\
  & Syn Scan & 99.1& \textbf{99.70} & 96.60 & 98.75\\
  & Fin Scan & 100 &                & 100 &\\ \hline

4 & UDP Flood & \textbf{26.6} & Avg = & \textbf{100} & Avg =\\
  & RCP Scan  & 91.56         & 70.35 & 92.60        & 98.15\\
  & Fin Scan  & 99.8          &       & 100          &\\ \hline

5 & Http Flood & 85.7& Avg =          & 100 & Avg =\\
  & RCP Scan  & 92.3 & \textbf{99.94} & 91.80 & 97.50\\
  & Fin Scan  & 99.8 &                & 98.20 &\\

\hline\end{tabular}
\label{tab:fuzGenExp2}
\end{table}

\subsubsection{Experiments using Both RLD09 and KDD99}
The authors of~\cite{6496342, 6559603} also ran experiments that compared the RLD09 data set with the KDD99 data set. They used the KDD99 10\% version file for both the training dataset and testing dataset. The number of records of normal and attack activity for the two data sets are shown in Table~\ref{tab:RecordsForKDD99}.

\begin{table}
\caption{Number of Records for KDD99}
\begin{tabular}{|lll|} \hline
Attack & Training & Testing\\
Type   & Data set & Data set\\ \hline
Normal & 39,387 & 39,337\\
DoS & 158,597 & 158,503\\
Probe & 1,550 & 1,674\\
 & &\\
 Total & 199,534 & 199,514\\

\hline\end{tabular}
\label{tab:RecordsForKDD99}
\end{table}
